Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-10-01 final_submission/manuscript.tex
Final commit. DONE BITCHES YEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE

\section{Conclusion}
	//TODO
\section{References}
	\begin{thebibliography}{9}
	\bibitem{areconnect}
		\url{http://ithaca.areaconnect.com/statistics.htm}
	\bibitem{CIC-stats}
		\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
	\bibitem{CIC-qa}
		\url{http://www.cdc.gov/h1n1flu/qa.htm}
	\bibitem{walph}
		Wolfram Research Inc.,
		\emph{WolframAlpha},
		Retrieved September 26, 2015
		\url{http://www.wolframalpha.com/input/?i=ds%2Fdt+%3D+r+s+%28K+-+s+-+a+t%29}
		\url{http://www.wolframalpha.com/input/?i=%E2%88%AB+e^%28-a+x^2+%2B+b+x%29+dx}
	\bibitem{SIR}
		\url{http://web.stanford.edu/~jhj1/teachingdocs/Jones-on-R0.pdf}
	\bibitem{applet}
		\url{http://www.public.asu.edu/~hnesse/classes/sirv.html?}
	\bibitem{NGM}
		\url{http://rsif.royalsocietypublishing.org/content/7/47/873}
	\bibitem{oneweek}
		\url{https://www.cdph.ca.gov/HealthInfo/h1n1flufaqs/Pages/H1N1fluFAQs-01-GenInfo.aspx}
	\bibitem{R0}
		\url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2715422/}
	\bibitem{deathgraph}
		\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
    \bibitem{init}
        \url{http://academic.udayton.edu/muhammadusman/2010Stander/H1N1.pdf}
    \bibitem{deathpercent}
        \url{http://www.cdc.gov/h1n1flu/estimates_2009_h1n1.htm}
    \bibitem{pop}
        \url{http://ithaca.areaconnect.com/statistics.htm}
	\end{thebibliography}

>>>>

\section{Conclusions}

A letter to the Ithaca Journal from the Modeling Department of the CDC:

\paragraph{}
This letter recommends a first-come first-serve
	vaccination policy in Ithaca during an epidemic.
My colleagues and I are epidemic modelers, and we have researched
	past flu outbreaks and used them to simulate how Ithaca
	would react to a flu outbreak.
Based on our research and modeling, we determined that if a
	flu epidemic strikes Ithaca suddenly, it is more important
	for all of the vaccines to be distributed than for us to
	vaccinate a particular population first.
We urge people to vaccinate before the outbreak, so that they are not
	vulnerable to the disease at the beginning.
By not vaccinating yourself, you not only risk catching the flu,
	you risk spreading it to others, possibly young children and the
	elderly who are less able to resist it.
We urge Cornell, Ithaca College, and the Tompkins County Public School
	System, to provide vaccination in class, especially before an epidemic.

It is important to vaccinate before an outbreak because vaccines are
	distributed to each reason on a monthly basis.
We must not waste our distributed portion of vaccines before the outbreak
	starts.
We recieve 4000 every month, and we want to make sure that people are
	ready for the flu season before it starts.
Therefore, everybody should be vaccinated, especially children and the elderly.

During an outbreak, we recommend that vaccines should be uniformly distributed
	between Cornell, Ithaca College, and Ithaca Proper.
Our models did not find a significant difference between distribution strategies,
	so we urge local officials and school administrators to estimate how
	many students they think they can vaccinate each month.
It is important that these valuable vaccinations not go to waste.

\section{References}
	\begin{thebibliography}{9}
	\bibitem{areconnect}
		\url{http://ithaca.areaconnect.com/statistics.htm}
	\bibitem{CIC-stats}
		\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
	\bibitem{CIC-qa}
		\url{http://www.cdc.gov/h1n1flu/qa.htm}
	\bibitem{walph}
		Wolfram Research Inc.,
		\emph{WolframAlpha},
		Retrieved September 26, 2015
		\url{http://www.wolframalpha.com/input/?i=ds%2Fdt+%3D+r+s+%28K+-+s+-+a+t%29}
		\url{http://www.wolframalpha.com/input/?i=%E2%88%AB+e^%28-a+x^2+%2B+b+x%29+dx}
	\bibitem{SIR}
		\url{http://web.stanford.edu/~jhj1/teachingdocs/Jones-on-R0.pdf}
	\bibitem{applet}
		\url{http://www.public.asu.edu/~hnesse/classes/sirv.html?}
	\bibitem{NGM}
		\url{http://rsif.royalsocietypublishing.org/content/7/47/873}
	\bibitem{oneweek}
		\url{https://www.cdph.ca.gov/HealthInfo/h1n1flufaqs/Pages/H1N1fluFAQs-01-GenInfo.aspx}
	\bibitem{R0}
		\url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2715422/}
	\bibitem{deathgraph}
		\url{http://www.cdc.gov/h1n1flu/surveillanceqa.htm}
    \bibitem{init}
        \url{http://academic.udayton.edu/muhammadusman/2010Stander/H1N1.pdf}
    \bibitem{deathpercent}
        \url{http://www.cdc.gov/h1n1flu/estimates_2009_h1n1.htm}
    \bibitem{pop}
        \url{http://ithaca.areaconnect.com/statistics.htm}
	\end{thebibliography}
